\section{Project Description}

    \subsection{Project Perspective}
        While the market for social markets is relatively saturated, there remain a
        few niches yet untouched. One such niche is an open source social network
        and another is a local, geographically aware social network. Beacon will
        enable people to discover events and places within their local community.

    \subsection{Functions}
        \subsubsection{View Map}
            After login, the frontend will display a map of the user's local area,
            on which is overlaid beacons in this area. From map view, the user may
            select individual beacons, which will cause a thumbnail of the beacon to
            appear. Selecting a thumbnail within map view will cause the frontend to
            switch to thread view.

        \subsubsection{Post Beacon}
            From camera view, the user may take a picture of their surroundings.
            Optionally, a description may accompany this picture. Upon confirmation,
            the beacon will be uploaded to the backend and made available for other
            users to view.
            
        \subsubsection{View Comment Thread}
            When a particular beacon is selected from map view, the comment thread for
            that beacon will be loaded. From thread view, the user may view all
            comments posted to a particular beacon and may post their own comment on
            the beacon. Additionally, the user may heart the beacon or any comments,
            as well as flag the beacon or any comments.

        \subsubsection{Heart Post}
           From thread view, a user may heart either a beacon or any of the comments
           associated with it. This is accomplished by selecting an icon in the shape
           of a heart. At any time, selecting the heart icon on a post that has already
           been hearted will cause the action of hearting to be rescinded.

        \subsubsection{Post Comment}
           From thread view, the user may post a comment. This is accomplished by
           selecting an icon, entering text, and confirming submission of the comment.
           Once submitted, the comment will become available for other users to view
           and heart.

        \subsubsection{View User Profile}
           From thread view, the user may select the username of the poster of the
           beacon or an associated comment. This will open profile view for that
           particular user. Displayed in profile view will be a list of all the beacons
           and comments posted by this user. An individual listing may be selected to
           opening the corresponding thread view for that particular post.

        \subsubsection{Follow User}
           From profile view for a particular user, one may select an icon in order
           to follow the user. This will cause a notification to be pushed whenever
           the followed user posts a beacon.

        \subsubsection{Flag Comment/Post}
            From thread view, the beacon or any of its corresponding comments may be
            flagged by a user as abusive by selecting a flag icon. This information
            will be submitted to the backend which will make a decision as to whether
            the post is actually abusive. If it decides that the post is abusive, the
            post will be removed.

        \subsubsection{Account Creation}
            Upon first installing the frontend, a user will be prompted to create an
            account. The system will authenticate using third party services such as
            Facebook, Google Accounts, or OpenID. Once authenticated by the third party,
            an account will be created in the Beacon backend associated with the
            authentication information provided by the third party service.
