\section{Introduction}
\paragraph*{}
    This document aims to express the requirements for the Beacon frontend and backend
    applications. This document describes the high-level and low-level requirements
    of these applications and the systems on which they will run. A team provided with
    this document and no other instruction should be capable of completely developing
    these applications.

\subsection{Goals}
\paragraph*{}
    The Beacon social network will provide an interface for anonymous users to post
    geotagged images along with descriptions. Additionally, Beacon will provide
    functionality by which users may discuss posts and express support for chosen
    posts. Beacon will provide an interface by which users may express their opinion
    that a post is abusive. The system will robustly decide whether a given post
    is actually abusive and, if so, prune it.

\subsection{Definitions}
\begin{itemize}
    \item \textbf{Frontend} - A mobile application providing all user-facing
        functionality of the Beacon social network. The frontend communicates
        with the backend in order to retrieve and update information.

    \item \textbf{Backend} - An application running on a remote server with which
        the Beacon frontend communicates in order to retrieve/update all remote
        data. The backend consists of a REST interface and a database.

    \item \textbf{Beacon} - A user-generated post consisting of an image, a geotag,
        a description, and comments submitted by other users. Beacons are presented
        to the user as icons overlaid on a map.

    \item \textbf{Hearting} - An action by which a user may demonstrate their support
        for a beacon or comment. This action is called "hearting" because it is
        carried out by selecting an icon in the shape of a heart.

    \item \textbf{Thread View} - A mode of operation of the Beacon frontend in which
        the comments for a specific beacon are visible.

    \item \textbf{Map View} - A mode of operation of the Beacon frontend in which
        local beacons are visible. From Map View, the user may pan and zoom to view
        different beacons.
        
    \item \textbf{Camera View} - A mode of operation of the Beacon frontend in which
        the user may take a picture and upload it as a new beacon.

    \item \textbf{Profile View} - A mode of operation of the Beacon frontend in which
        the past beacons and comments posted by an individual user are listed.

\end{itemize}
    
