\section{Document Modification Process}
\paragraph*{}
    A formal change management procedure will be followed whenever modifications
    to this document become necessary. This document is intended to be written in
    \LaTeX and kept under
    Git version control. When changes are commited to version control, a record
    of the changes will automatically be recorded to the revision history within this document and the
    revision number will automatically be updated accordingly. If a modification to this document
    locally consists of multiple commits, it is recommended that these commits be
    squashed into one commit with a meaningful message before being checked into a
    remote repository.

\paragraph*{}
    Proposed changes shall be reviewed via pull request. Once
    accepted, the branch containing the proposed changes shall be merged to master. 
    Additionally a binary repository containing the PDF file outputs for each official revision
    shall be made available to all members of the development team. This repository
    shall be updated automatically upon modification of the master branch. The revision     number of this document shall be updated according to the following rules:

    \begin{enumerate}
        \item Changes that substantially alter the content of this document shall
                increment the major version number. A commit message containing the
                string "major" (not case-sensitive) will automatically increment this
                number.
        \item Changes that alter the content of this document shall increment the
                minor version number. A commit message containing the string "minor"
                (not case-sensitive) will automatically increment this number.
        \item Any changes that do not alter the content of this document and make
                merely cosmetic changes shall increment the patch number.
                Any commit message not containing the string "major" or "minor" shall be
                considered a patch and the patch number will be
                incremented automatically when committed.
    \end{enumerate}
